Sparsity Weak Lensing $3$-D Density Map Reconstruction

### 2020-10-10 doc/paper_ms_method_HSCY1/ms.tex
add figures to paper

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast fields from photometric weak lensing shear measurements.
The $3$-D density contrast map is modeled as a superposition of basis atoms. The basis atoms are designed to represent 
the structure of NFW halos which have $2$-D multi-scale NFW surface density profiles on the transverse plane and $1$-D 
Dirac delta functions in the line-of-sight direction. With the prior assumption that the basis atoms have a spare distribution, 
the density field is reconstructed using the adaptive lasso algorithm. The method is tested with realistic simulation 
using HSC-like shape noise and photo-$z$ uncertainties. 
{\redColor{Add descriptions on the outcomes of the test on the simulations.}}
\end{abstract}

\section{Introduction}
Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
sheared. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
to the background galaxy images and offers a direct probe into the mass density distribution in our universe
\citep[see][for recent reviews]{revKilbinger15,revRachel17}.

Adopting the thin lens approximation, the expected shear measurements ($\gamma$) on distant galaxies are related to the 
foreground density contrast field ($\delta$) through a linear transformation
\begin{equation} \label{eq-intro-delta2shear}
 \gamma=\mathbf{T} \delta,
\end{equation}
where $\mathbf{T}$ is used to denote the linear transformation operator which includes not only physical lensing effect
but also includes observational systematic effects from the observation (e.g. pixelization and smoothing of shear field in
transverse plane, photo-$z$ uncertainties).

@@

Reconstructions of density map from shear measurements also receive considerable interest. $2$-D density map reconstruction 
which reconstructs the integration of mass along the line-of-sight direction has been well studied by the community
\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016}
and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}.

In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the tomographic shear observations ($\gamma$),
the density contrast field is modeled as a superposition of basis atoms in a dictionary space
\begin{equation} \label{eq-intro-dict}
 \delta= \mathbf{\Phi} x,
\end{equation}
where $\mathbf{\Phi}$ is the transformation operator from the parameters in the dictionary space to the density contrast 
and $x$ denotes the parameters in the dictionary space. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
in Fourier space, which is equivalent to model the mass field with sinusoidial functions. On the other hand,
\citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass field with Starlets.

@@

\citet{LSS-massMap-Wiener-Simon2009} propose to use the $l^2$ ridge regulation ($C=\norm{x}^2_2$) to find the best-fit 
solution in Fourier space. \citet{HSC1-massMaps} apply the method of \citet{LSS-massMap-Wiener-Simon2009} to the first 
year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
{\redColor{Why we use $l^1$ in this paper, what is the difference between $l^1$ and $l^2$.}}

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use the $l^1$ lasso regulation ($C=\norm{x}^1_1$) to find the
best-fits solution in a Starlets dictionary space. However, the Starlets functions are not designed to model the 
clumpy mass distributions in the universe and \citet{LSS-massMap-Glimpse3D-Leonard2014} use a greedy descent algorithm 
to find minima of the loss function, which is not guarateed to converge to the global minima ({\redColor{cite..}}).

$N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density 
distribution of a halo follows the NFW profile \citep{halo-NFW1997ApJ}.
We construct a dictionary which is composed of multi-scale NFW atoms and point mass atoms. The multi-scale NFW atoms are used 
to model the structures within halos. They follow multi-scale surface density profiles of NFW halos \citep{haloModel-TJ2003-3pt}
on the transverse plane and Dirac delta function in the line-of-sight direction. By using Dirac delta functions in the 
line-of-sight direction, the depth of halo is neglected \citep{LSS-massMap-Glimpse3D-Leonard2014} since the resolution 
scale of the reconstruction in the line-of-sight direction is much larger than the halo scale.
The point mass atoms are used to model the structures in the filaments and structures smaller than the reachable resolution
on the transverse plane. Furthermore, the point mass atoms make our dictionary space complete.
With the prior assumption that the density contrast field is sparse in the dictionary space, the adaptive lasso regularization
\citep{AdaLASSO-Zou2006} is used to reconstruct a high signal-to-noise-ratio (SNR) density contrast field.

Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary space is built up to describe the clumpy mass 
in the universe which has clear physical a motivation. Moreover, we use adaptive lasso which does not rely on any greedy 
descent alorithm, therefore the estimation is guarateed to converge to the global minimum.

@@

In this section, we first review how foreground density distributions induce weak lensing shear distortions on background
galaxies in section \ref{subsec:method-delta2shear}.
Then, we introduce the dictionary space used to model the foreground density map in section \ref{subsec:method-dictionary}.

Subsequently, in section \ref{subsec:method-Systematics} we discuss several systematic effects from observations which include 
photo-$z$ uncertainty (section \ref{subsec:method-photoz}),
smoothing (section \ref{subsec:method-smoothing}),
masking(section \ref{subsec:method-msknoise}),
and pixelization (section \ref{subsec:method-pixel}).

@@

\begin{figure*}
    \includegraphics[width=0.95\textwidth]{nfwlet-atom-2D.pdf}
    \caption{The NFW models with different scale radius ($r_s$). The first row shows the NFW models in Fourier
            space and the second row shows the NFW model in Real space.}
\end{figure*}

The lensing convergence $\kappa$ at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
\citep{LSS-massMap-Glimpse3D-Leonard2014}
\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
\end{equation}
where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed
of light, and $a(\chi_l)$ is the scale parameter at the lens position.

@@

Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the physical shear signal is derived as
\begin{equation}\label{eq-delta2gammat}
\gamma_L(\vec{\theta},z_s) = \int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
\end{equation}

To simplify the expression, we define the lensing transform operator as
\begin{equation}
\mathbf{Q}=\int_0^{z_s} \frac{dz_l}{\delta_{c}(z_l,z_s)} \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
\end{equation}
and eq. (\ref{eq-delta2gammat}) is simplified to
\begin{equation} \label{eq-delta2gammat-simp}
\gamma_L=\mathbf{Q}\delta.
\end{equation}

\subsection{Dictionary}
\label{subsec:method-dictionary}
\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
        are the bounds of bins. The galaxies are evenly distributed in each bins.}
\end{figure}

The density contrast field is modeled as a superposition of basis atoms in the dictionary space $\{\phi_0,\phi_1,...\phi_{N}\}$.
\begin{equation}\label{eq-x2delta}
\delta(\vec{r}) = \sum_{s=0}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
\end{equation}
where $\phi_s(\vec{r})$ is the basis vector of the dictionary space, and $x_s$ is the corresponding projection
coefficients of the density contrast field onto the basis vectors.

@@

\subsubsection{Photo-$z$ Uncertainty}
\label{subsec:method-photoz}
\begin{figure}
 \includegraphics[width=0.5\textwidth]{nfwlet-atom-1D.pdf}
 \caption{The $1$-D slices of NFW models with different scale radius ($r_s=0,1,2,4,8$).}
\end{figure}

@@

\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different coefficients 
in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. Lasso estimation is performed in the first step 
and achieve a preliminary lasso estimation of parameter ($\hat{x'}^{\rm{lasso}}$). In the second step, the lasso estimation is used 
to weight the penalization on the parameters. With the definition of the adaptive lasso weight 
\begin{equation}
\hat{w}= \frac{1}{\abs{\hat{x'}^{\rm{lasso}}}^\tau},
\end{equation}
here we set the hyper-parameter $\tau$ to $2$, the adaptive lasso estimator is expressed as
\begin{equation}\label{eq-lossFun}
\hat{x'}=\argmin_{x'} \left\{ \frac{1}{2} \norm{\Sigma^{-\frac{1}{2}}(\gamma-\mathbf{A'}x')}^2_2 +
\hat{w}\lambda \norm{x'}^1_1\right\}.
\end{equation}

@@

\section{Simulation}
\label{sec:Sim}
This section simulates lensing shear fields induced by a group of dark matter halos with various halo mass and redshifts.
HSC-like shape measurement error and photo-$z$ error are added to the shear field.

@@

We simulate weak lensing shear fields of NFW halos according to \citet{haloModel-TJ2003-3pt}
and sample halos in the mass-redshift plane as shown in Figure \ref{fig:mass-redshift}.
We assume a dependency of the concentration on the mass and the redshift of a halo as \citep{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}

\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{mass-redshift-sampling.pdf}
 \caption{The sampling points of halos in the mass-redshift plane.}
 \label{fig:mass-redshift}
\end{figure}

\subsection{HSC-like Systematic}
\subsubsection{Shear Measurement Error}
\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{HSC-like measurement error on the first component of shear ($g_1$).}
 \label{fig:mass-redshift}
\end{figure}

\subsubsection{Photo-$z$ Error}

@@

\bibliographystyle{aasjournal}
\bibliography{citation}

>>>>

\begin{abstract}
A new method is developed to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
The $3$-D density contrast maps is modeled as a summation of basis atoms which are designed to represent the profiles of 
multi-scale NFW halos. The NFW atoms have $2$-D multi-scale NFW surface density profiles on the transverse plane and 
$1$-D Dirac delta functions in the line-of-sight direction. With the sparsity prior assumption, the density field 
is reconstructed using an oracle algorithm: adaptive lasso. Our method is tested with realistic simulations using HSC-like 
shape noise and photo-$z$ uncertainties.
{\redColor{Add descriptions on the outcomes of the test on the simulations.}}
\end{abstract}

\section{Introduction}

\begin{figure*}[!ht]
    \includegraphics[width=0.98\textwidth]{nfwlet-atom-2D.pdf}
    \caption{The smoothed basis atoms with different scale radius ($r_s$). The first row shows the smoothed basis atoms in 
            Fourier space and the second row shows the smoothed basis atoms in Real space. The smoothing kernel is Gaussian
            with scale of $1.5$ pixels.} \label{fig-atoms2D}
\end{figure*}

\begin{figure}
 \includegraphics[width=0.45\textwidth]{nfwlet-atom-1D.pdf}
 \caption{The $1$-D slices for smoothed basis atoms at $x=0$. The corresponding $2$-D profiles are shown in Figure 
            \ref{fig-atoms2D}.}
\end{figure}

Light from distant galaxies is distorted by the intervening inhomogeneous density distribution along the line-of-sight
due to the influence of gravity. As a result of the light distortion, the shapes of the background galaxies are coherently
sheared. Such effect, which is known as weak lensing, imprints the information of foreground mass density distribution
to the background galaxy images and offers a direct probe into the mass density distribution in our universe
\citep[see][for recent reviews]{revKilbinger15,revRachel17}.

Adopting the thin lens approximation, the expected shear measurements ($\gamma$) on distant galaxies are related to the 
foreground density contrast field ($\delta$) through a linear transformation
\begin{equation} \label{eq-intro-delta2shear}
 \gamma=\mathbf{T} \delta,
\end{equation}
where $\mathbf{T}$ is used to denote the linear transformation operator which includes not only physical lensing effect
but also observational systematic effects from the observation (e.g. pixelization and smoothing of shear field in
transverse plane, photo-$z$ uncertainties).

@@

Reconstructions of density map from shear measurements also receive considerable interest. $2$-D density map reconstruction 
which recover an integration of projected mass along the line-of-sight has been well studied within the community
\citep{massMap-KS1993,WL-massMap-Glimpse2D-Lanusse2016}
and applied to large scale surveys \citep{HSC1-massMaps,massMapDES-Chang2018,DES-SV-massMap-sparsity}. However, the 
reconstruction of $3$-D mass map is still a challenging task.

In order to fully reconstruct the $3$-D mass density distribution ($\delta$) from the tomographic shear observations ($\gamma$),
the density contrast field is modeled as a summation of basis atoms in a model dictionary
\begin{equation} \label{eq-intro-dict}
 \delta= \mathbf{\Phi} x,
\end{equation}
where $\mathbf{\Phi}$ is the transformation operator from the parameters in the dictionary space to the density contrast 
and $x$ denotes the parameters. \citet{LSS-massMap-Wiener-Simon2009} reconstruct the density field
in Fourier space, which is equivalent to model the mass field with sinusoidial functions. On the other hand,
\citet{LSS-massMap-Glimpse3D-Leonard2014} models the mass field with Starlets \citep{Starlet-Starck2015}.

@@

\citet{LSS-massMap-Wiener-Simon2009} propose to use the $l^2$ ridge regulation ($C=\norm{x}^2_2$) to find a sparse 
solution in Fourier space. \citet{HSC1-massMaps} apply the method of \citet{LSS-massMap-Wiener-Simon2009} to the first 
year data of the Hyper Suprime-Cam Survey \citep{HSC1-data}. 
{\redColor{Why we use $l^1$ in this paper, what is the difference between $l^1$ and $l^2$.}}

\citet{LSS-massMap-Glimpse3D-Leonard2014} propose to use a derivative version of $l^1$ lasso regulation ($C=\norm{x}^1_1$) 
to find a sparse solution in the Starlets dictionary space \citep{Starlet-Starck2015}. However, the Starlets functions are 
not designed to model the profile of clumpy mass in the universe. Moreover, \citet{LSS-massMap-Glimpse3D-Leonard2014} 
apply a greedy coordinate descent algorithm, which selects the steepest coordinate in each iteration, find the minima of 
a non-convex loss function. However, the stability of the non-convex optimization has not been fully discussed.

$N$-body simulations have shown that the dark matter is distributed in halos connected by filaments, and the density 
profile of a single halo follows the NFW function \citep{halo-NFW1997ApJ}.
We construct a dictionary which is composed of multi-scale NFW atoms. The multi-scale NFW atoms are used to model the 
profiles of halos. The atoms follow multi-scale surface density profiles of NFW functions \citep{haloModel-TJ2003-3pt}
on the transverse plane.
The depth of halo is neglected \citep{LSS-massMap-Glimpse3D-Leonard2014} since the resolution scale of the reconstruction 
in the line-of-sight direction is much larger than the halo scale. Therefore, the Dirac delta function is used to model the
atoms' profile in the line-of-sight direction. 
With the prior assumption that the density contrast field is sparse in the dictionary space, the adaptive lasso regularization
\citep{AdaLASSO-Zou2006} is used to reconstruct a high signal-to-noise-ratio (SNR) density contrast field.

Comparing with \citet{LSS-massMap-Glimpse3D-Leonard2014}, our dictionary is built up to describe the clumpy mass 
in the universe which has a clear physical motivation. Furthermore, the adaptive lasso algorithm is full convex and 
can be optimized with the FISTA algorithm \citep{FISTA-Beck2009} without relying on any greedy coordinate descent approaches. 
The stability of this convex optimization has been well studied.

@@

We first review the lensing process in section \ref{subsec:method-delta2shear}.
Then, we introduce the dictionary used to model the foreground density maps in section \ref{subsec:method-dictionary}.

Subsequently, in section \ref{subsec:method-Systematics}, we discuss several systematic effects from observations which 
include photo-$z$ uncertainty (section \ref{subsec:method-photoz}),
smoothing (section \ref{subsec:method-smoothing}),
masking(section \ref{subsec:method-msknoise}),
and pixelization (section \ref{subsec:method-pixel}).

@@

The lensing convergence map at the comoving distance $\chi_s$ caused by the foreground inhomogeneous
density distribution at the comoving distance $\chi_l$ ($\chi_l< \chi_s$) along the line-of-sight is
\citep{LSS-massMap-Glimpse3D-Leonard2014}
\begin{equation}
\kappa(\vec{\theta},\chi_s)=\frac{3H_0^2\Omega_M}{2 c^2} \int_0^{\chi_s} d\chi_l \frac{\chi_l \chi_{sl}}{\chi_s}
\frac{\delta(\vec{\theta},\chi_l)}{a(\chi_l)},
\end{equation}
where $\delta=\rho(\vec{\theta},\chi_l)/\bar{\rho}-1$ is the density contrast
at the position of lens, $H_0$ is the Hubble parameter, $\Omega_M$ is the matter density parameter, $c$ is the speed
of light, and $a(\chi_l)$ is the scale parameter at the lens position.

@@

Combining equation (\ref{eq-delta2kappa}) with equation (\ref{eq-kappa2gamma}), the physical shear signal is derived as
\begin{equation}\label{eq-delta2gammat}
\gamma_L(\vec{\theta},z_s) = \int_0^{z_s} dz_l K(z_l,z_s) \int d^2 \theta' \vec{D}(\vec{\theta}-\vec{\theta'}) \delta(\vec{\theta'},z_l).
\end{equation}

To simplify the expression, we define the lensing transform operator as
\begin{equation}
\mathbf{Q}=\int_0^{z_s} dz_l K(z_l,z_s) \int d^2 \theta'  \vec{D}(\vec{\theta}-\vec{\theta'}),
\end{equation}
and eq. (\ref{eq-delta2gammat}) is simplified to
\begin{equation} \label{eq-delta2gammat-simp}
\gamma_L=\mathbf{Q}\delta.
\end{equation}

\subsection{Dictionary}
\label{subsec:method-dictionary}

The density contrast field is modeled as a summation of basis atoms in the dictionary space $\{\phi_0,\phi_1,...\phi_{N}\}$.
\begin{equation}\label{eq-x2delta}
\delta(\vec{r}) = \sum_{s=0}^{N} \int d^3 r' \phi_s(\vec{r}-\vec{r'}) x_s(\vec{r'}),
\end{equation}
where $\phi_s(\vec{r})$ is the basis vector of the dictionary space, and $x_s$ is the corresponding projection
coefficients of the density contrast field onto the basis vectors.

@@

\subsubsection{Photo-$z$ Uncertainty}
\label{subsec:method-photoz}

\begin{figure}
 \centering
 \includegraphics[width=0.5\textwidth]{photo-z_binning.pdf}
 \caption{The source galaxies are binned into $10$ redshift bins according to their mlz best photo-$z$ estimation.
        The blue histogram is the number distribution of the best photo-$z$ estimation. The vertical dashed lines
        are the bounds of bins. The galaxies are evenly distributed in each bins.}
\end{figure}

@@

\citet{AdaLASSO-Zou2006} proposes the adaptive lasso algorithm which uses adaptive weights to penalize different coefficients 
in the $l^1$ penalty. The addaptive lasso algorithm is a two-steps process. First, Lasso estimation is performed in the first 
step and achieve a preliminary lasso estimation of parameter ($\hat{x'}^{\rm{lasso}}$). In the second step, the lasso estimation 
is used to weight the penalization on the parameters. With the definition of the adaptive lasso weight 
\begin{equation}
\hat{w}= \frac{1}{\abs{\hat{x'}^{\rm{lasso}}}^\tau},
\end{equation}
here we set the hyper-parameter $\tau$ to $2$, the adaptive lasso estimator is expressed as
\begin{equation}\label{eq-lossFun}
\hat{x'}=\argmin_{x'} \left\{ \frac{1}{2} \norm{\Sigma^{-\frac{1}{2}}(\gamma-\mathbf{A'}x')}^2_2 +
\hat{w}\lambda \norm{x'}^1_1\right\}.
\end{equation}

@@

\section{Simulation}
\label{sec:Sim}

This section simulates lensing shear fields induced by a group of dark matter halos with various halo masses and redshifts.
Then the shear distortions are applied to HSC mock catalogs with different realizations of HSC-like shape noises and photo-$z$
uncertainties.

The $\Lambda$CDM cosmology used for the simulations is from the best fitting result of the final full-mission Planck observation 
of the cosmic microwave background (CMB) with $H_0=67.4 ~\rm{km~s^{-1} Mpc^{-1}}$ $\Omega_M=0.315$, $\Omega_\Lambda=0.685$
\citep{cmb-Planck2018-Cosmology}.

@@

We sample halos in two dimensional (mass, redshift) plane. The two dimensional plane is divided into eight redshift bins 
times eight mass bins. The input redshifts and masses are shifted by random values for each halo, respectively.

We simulate weak lensing shear fields of NFW halos according to \citet{haloModel-TJ2003-3pt}
We assume a dependency of the concentration on the mass and the redshift of a halo 
\citet[equation (2)]{c-M_Magneticum-Ragagnin2019}
\begin{equation}
c_{h}=6.02\times(\frac{M_{200}}{10^{13} M_{\odot}})^{-0.12}(\frac{1.47}{1.+z_h})^{0.16}.
\end{equation}

\subsection{HSC mock Catalog}
\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{shapeMeasurementError-HSCY1.pdf}
 \caption{HSC-like measurement error on the first component of shear ($g_1$).}
 \label{fig:mass-redshift}
\end{figure}

For each galaxy, we randomly assign its redshift following the MLZ photo-$z$ probability distribution function 
\citep{HSC1-photoz} of the galaxy. The shear values are obtained from the all-sky weak lensing maps at two adjacent 
redshift slices with linearly interpolation.

@@

We develope a novel method to reconstruct $3$-D density contrast maps from photometric weak lensing shear measurements.
Our method models $3$-D density contrast maps as a summation of NFW atoms with multiple comoving radius and point mass atoms
in the $3$-D space binned with photometric redshift. The NFW atoms are used to model the mass in isolated halos and the 
point mass atoms are used to model the structures close to the resolution limit of the reconstruction.

With the prior assumption that the basis atoms sparsely distributes in the $3$-D space, the density field is reconstructed 
using the adaptive lasso algorithm \citep{AdaLASSO-Zou2006} which has the oracle properties.

The method is tested with realistic simulations using HSC-like shape noise and photo-$z$ uncertainties.

\begin{figure*}[!ht]
 \centering
 \includegraphics[width=0.95\textwidth]{detfalseRate_f1-1.pdf}
 \includegraphics[width=0.95\textwidth]{detfalseRate_f1-3.pdf}
 \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
point mass atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
\end{figure*}

\begin{figure*}[!ht]
 \centering
 \includegraphics[width=0.95\textwidth]{detfalseRate_f3-1.pdf}
 \includegraphics[width=0.95\textwidth]{detfalseRate_f3-3.pdf}
 \caption{The upper panels show the detection rate and false peak per square degree for mass map reconstruction with
NFW atoms and $\lambda=3.5$. The low panels show the results for $\lambda=5.0$. }
\end{figure*}

\begin{figure*}[!ht]
 \centering
 \includegraphics[width=0.95\textwidth]{peak_scatters_f3-1.pdf}
 \caption{The left panel shows the stacked distribution of deviations of detected peak positions 
 from the centers of the corresponding input halos. The $x$-axis is for the deviated distance in the transverse plane and the 
 $y$-axis is for the deviation of the redshift. The peaks inside the dashed black box are regarded as true detections. The 
 right panel focus on the deviation of detected peaks in the line-of-sight direction. The $x$-axis shows the input redshifts 
 and the $y$-axis is the redshift of the detected peak. The cross symbols show the average redshift of detected peak for 
 halos with different input redshift and mass and the error-bars are the scatter of the corresponding peak redshifts. All 
 of the results in this figure are based on the NFW atoms.}
\end{figure*}

\begin{figure}[!ht]
 \centering
 \includegraphics[width=0.45\textwidth]{peak_histograms.pdf}
 \caption{The histograms of detected peak values for all of the halo and error realizations. The dotted lines with different 
 colors are for the results of reconstruction with NFW atoms dictionary penalized with different regularization parameter 
 $\lambda$.}
\end{figure}

\clearpage
\bibliographystyle{aasjournal}
\bibliography{citation}
